Towards Practical First-Order Model Counting

### 2025-01-24 doc/paper/plot.tex
Resize the figure

% Created by tikzDevice version 0.12.6 on 2024-08-07 14:16:35
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (505.89,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (186.23,198.75);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 33.14, 57.56) rectangle (186.23,198.75);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14, 70.17) --
	(186.23, 70.17);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,101.68) --
	(186.23,101.68);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,133.19) --
	(186.23,133.19);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,164.70) --
	(186.23,164.70);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,196.21) --
	(186.23,196.21);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 42.89, 57.56) --
	( 42.89,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 81.85, 57.56) --
	( 81.85,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (120.82, 57.56) --
	(120.82,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (159.78, 57.56) --
	(159.78,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14, 85.92) --
	(186.23, 85.92);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,117.43) --
	(186.23,117.43);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,148.95) --
	(186.23,148.95);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,180.46) --
	(186.23,180.46);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 62.37, 57.56) --
	( 62.37,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (101.34, 57.56) --
	(101.34,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (140.30, 57.56) --
	(140.30,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (179.27, 57.56) --
	(179.27,198.75);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.10,106.36) --
	( 45.67,106.36) --
	( 51.24,106.36) --
	( 56.80,106.36) --
	( 62.37,106.36) --
	( 67.94,106.37) --
	( 73.50,106.38) --
	( 79.07,106.42) --
	( 84.64,106.58) --
	( 90.20,107.23) --
	( 95.77,109.99) --
	(101.34,117.90);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 40.10,123.48) --
	( 45.67,112.22) --
	( 51.24,112.22) --
	( 56.80,112.42) --
	( 62.37,119.02) --
	( 67.94,162.96);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 40.10,106.36) circle (  1.96);

\path[fill=fillColor] ( 45.67,106.36) circle (  1.96);

\path[fill=fillColor] ( 51.24,106.36) circle (  1.96);

\path[fill=fillColor] ( 56.80,106.36) circle (  1.96);

\path[fill=fillColor] ( 62.37,106.36) circle (  1.96);

\path[fill=fillColor] ( 67.94,106.37) circle (  1.96);

\path[fill=fillColor] ( 73.50,106.38) circle (  1.96);

\path[fill=fillColor] ( 79.07,106.42) circle (  1.96);

\path[fill=fillColor] ( 84.64,106.58) circle (  1.96);

\path[fill=fillColor] ( 90.20,107.23) circle (  1.96);

\path[fill=fillColor] ( 95.77,109.99) circle (  1.96);

\path[fill=fillColor] (101.34,117.90) circle (  1.96);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 38.14,121.52) --
	( 42.06,121.52) --
	( 42.06,125.44) --
	( 38.14,125.44) --
	cycle;

\path[fill=fillColor] ( 43.71,110.26) --
	( 47.63,110.26) --
	( 47.63,114.18) --
	( 43.71,114.18) --
	cycle;

\path[fill=fillColor] ( 49.27,110.26) --
	( 53.20,110.26) --
	( 53.20,114.18) --
	( 49.27,114.18) --
	cycle;

\path[fill=fillColor] ( 54.84,110.46) --
	( 58.76,110.46) --
	( 58.76,114.38) --
	( 54.84,114.38) --
	cycle;

\path[fill=fillColor] ( 60.41,117.06) --
	( 64.33,117.06) --
	( 64.33,120.99) --
	( 60.41,120.99) --
	cycle;

\path[fill=fillColor] ( 65.97,161.00) --
	( 69.90,161.00) --
	( 69.90,164.92) --
	( 65.97,164.92) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.54, 57.56) -- ( 34.54, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.10, 57.56) -- ( 40.10, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 45.67, 57.56) -- ( 45.67, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 51.24, 57.56) -- ( 51.24, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 56.80, 57.56) -- ( 56.80, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 62.37, 57.56) -- ( 62.37, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 67.94, 57.56) -- ( 67.94, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 73.50, 57.56) -- ( 73.50, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 79.07, 57.56) -- ( 79.07, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 84.64, 57.56) -- ( 84.64, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 90.20, 57.56) -- ( 90.20, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 95.77, 57.56) -- ( 95.77, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (101.34, 57.56) -- (101.34, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (106.90, 57.56) -- (106.90, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (112.47, 57.56) -- (112.47, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (118.04, 57.56) -- (118.04, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (123.60, 57.56) -- (123.60, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (129.17, 57.56) -- (129.17, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (134.74, 57.56) -- (134.74, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (140.30, 57.56) -- (140.30, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (145.87, 57.56) -- (145.87, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.44, 57.56) -- (151.44, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (157.00, 57.56) -- (157.00, 63.25);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (168.13, 57.56) -- (168.13, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (173.70, 57.56) -- (173.70, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (179.27, 57.56) -- (179.27, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.83, 57.56) -- (184.83, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 64.92) -- ( 38.84, 64.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 75.42) -- ( 38.84, 75.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 85.92) -- ( 38.84, 85.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 96.43) -- ( 38.84, 96.43);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,106.93) -- ( 38.84,106.93);

>>>>

% Created by tikzDevice version 0.12.6 on 2025-01-24 14:00:20
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,144.54);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (361.35,144.54);
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (138.05,126.48);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 33.14, 57.56) rectangle (138.05,126.48);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14, 63.71) --
	(138.05, 63.71);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14, 79.10) --
	(138.05, 79.10);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14, 94.48) --
	(138.05, 94.48);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,109.86) --
	(138.05,109.86);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,125.24) --
	(138.05,125.24);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 39.82, 57.56) --
	( 39.82,126.48);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 66.52, 57.56) --
	( 66.52,126.48);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 93.22, 57.56) --
	( 93.22,126.48);

\path[draw=drawColor,line width= 0.2pt,line join=round] (119.93, 57.56) --
	(119.93,126.48);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14, 71.41) --
	(138.05, 71.41);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14, 86.79) --
	(138.05, 86.79);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,102.17) --
	(138.05,102.17);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,117.55) --
	(138.05,117.55);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 53.17, 57.56) --
	( 53.17,126.48);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 79.87, 57.56) --
	( 79.87,126.48);

\path[draw=drawColor,line width= 0.5pt,line join=round] (106.58, 57.56) --
	(106.58,126.48);

\path[draw=drawColor,line width= 0.5pt,line join=round] (133.28, 57.56) --
	(133.28,126.48);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.91, 89.74) --
	( 41.73, 84.24) --
	( 45.54, 84.24) --
	( 49.36, 84.34) --
	( 53.17, 87.56) --
	( 56.99,109.01);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 37.91, 81.38) --
	( 41.73, 81.38) --
	( 45.54, 81.38) --
	( 49.36, 81.38) --
	( 53.17, 81.38) --
	( 56.99, 81.38) --
	( 60.80, 81.39) --
	( 64.62, 81.41) --
	( 68.43, 81.49) --
	( 72.24, 81.81) --
	( 76.06, 83.15) --
	( 79.87, 87.02);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 35.95, 79.42) --
	( 39.87, 79.42) --
	( 39.87, 83.35) --
	( 35.95, 83.35) --
	cycle;

\path[fill=fillColor] ( 39.77, 79.42) --
	( 43.69, 79.42) --
	( 43.69, 83.35) --
	( 39.77, 83.35) --
	cycle;

\path[fill=fillColor] ( 43.58, 79.42) --
	( 47.50, 79.42) --
	( 47.50, 83.35) --
	( 43.58, 83.35) --
	cycle;

\path[fill=fillColor] ( 47.39, 79.42) --
	( 51.32, 79.42) --
	( 51.32, 83.35) --
	( 47.39, 83.35) --
	cycle;

\path[fill=fillColor] ( 51.21, 79.42) --
	( 55.13, 79.42) --
	( 55.13, 83.35) --
	( 51.21, 83.35) --
	cycle;

\path[fill=fillColor] ( 55.02, 79.42) --
	( 58.95, 79.42) --
	( 58.95, 83.35) --
	( 55.02, 83.35) --
	cycle;

\path[fill=fillColor] ( 58.84, 79.43) --
	( 62.76, 79.43) --
	( 62.76, 83.35) --
	( 58.84, 83.35) --
	cycle;

\path[fill=fillColor] ( 62.65, 79.45) --
	( 66.58, 79.45) --
	( 66.58, 83.37) --
	( 62.65, 83.37) --
	cycle;

\path[fill=fillColor] ( 66.47, 79.53) --
	( 70.39, 79.53) --
	( 70.39, 83.45) --
	( 66.47, 83.45) --
	cycle;

\path[fill=fillColor] ( 70.28, 79.84) --
	( 74.21, 79.84) --
	( 74.21, 83.77) --
	( 70.28, 83.77) --
	cycle;

\path[fill=fillColor] ( 74.10, 81.19) --
	( 78.02, 81.19) --
	( 78.02, 85.11) --
	( 74.10, 85.11) --
	cycle;

\path[fill=fillColor] ( 77.91, 85.05) --
	( 81.84, 85.05) --
	( 81.84, 88.98) --
	( 77.91, 88.98) --
	cycle;
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 37.91, 89.74) circle (  1.96);

\path[fill=fillColor] ( 41.73, 84.24) circle (  1.96);

\path[fill=fillColor] ( 45.54, 84.24) circle (  1.96);

\path[fill=fillColor] ( 49.36, 84.34) circle (  1.96);

\path[fill=fillColor] ( 53.17, 87.56) circle (  1.96);

\path[fill=fillColor] ( 56.99,109.01) circle (  1.96);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.10, 57.56) -- ( 34.10, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 37.91, 57.56) -- ( 37.91, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.73, 57.56) -- ( 41.73, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 45.54, 57.56) -- ( 45.54, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.36, 57.56) -- ( 49.36, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 53.17, 57.56) -- ( 53.17, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 56.99, 57.56) -- ( 56.99, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 60.80, 57.56) -- ( 60.80, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 64.62, 57.56) -- ( 64.62, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 68.43, 57.56) -- ( 68.43, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.24, 57.56) -- ( 72.24, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 76.06, 57.56) -- ( 76.06, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 79.87, 57.56) -- ( 79.87, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 83.69, 57.56) -- ( 83.69, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 87.50, 57.56) -- ( 87.50, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 91.32, 57.56) -- ( 91.32, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 95.13, 57.56) -- ( 95.13, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 98.95, 57.56) -- ( 98.95, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (102.76, 57.56) -- (102.76, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (106.58, 57.56) -- (106.58, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (110.39, 57.56) -- (110.39, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (114.21, 57.56) -- (114.21, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (118.02, 57.56) -- (118.02, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (121.83, 57.56) -- (121.83, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (125.65, 57.56) -- (125.65, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (129.46, 57.56) -- (129.46, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (133.28, 57.56) -- (133.28, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (137.09, 57.56) -- (137.09, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 61.15) -- ( 38.84, 61.15);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 66.28) -- ( 38.84, 66.28);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 71.41) -- ( 38.84, 71.41);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 76.53) -- ( 38.84, 76.53);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 81.66) -- ( 38.84, 81.66);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 86.79) -- ( 38.84, 86.79);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 91.91) -- ( 38.84, 91.91);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 97.04) -- ( 38.84, 97.04);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,102.17) -- ( 38.84,102.17);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,107.30) -- ( 38.84,107.30);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,112.42) -- ( 38.84,112.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,117.55) -- ( 38.84,117.55);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,122.68) -- ( 38.84,122.68);
\end{scope}
\begin{scope}
\path[clip] (142.55, 57.56) rectangle (247.45,126.48);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (142.55, 57.56) rectangle (247.45,126.48);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] (142.55, 63.71) --
	(247.45, 63.71);

\path[draw=drawColor,line width= 0.2pt,line join=round] (142.55, 79.10) --
	(247.45, 79.10);

\path[draw=drawColor,line width= 0.2pt,line join=round] (142.55, 94.48) --
	(247.45, 94.48);

\path[draw=drawColor,line width= 0.2pt,line join=round] (142.55,109.86) --
	(247.45,109.86);

\path[draw=drawColor,line width= 0.2pt,line join=round] (142.55,125.24) --
	(247.45,125.24);

\path[draw=drawColor,line width= 0.2pt,line join=round] (149.22, 57.56) --
	(149.22,126.48);

\path[draw=drawColor,line width= 0.2pt,line join=round] (175.92, 57.56) --
	(175.92,126.48);

\path[draw=drawColor,line width= 0.2pt,line join=round] (202.63, 57.56) --
	(202.63,126.48);

\path[draw=drawColor,line width= 0.2pt,line join=round] (229.33, 57.56) --
	(229.33,126.48);

\path[draw=drawColor,line width= 0.5pt,line join=round] (142.55, 71.41) --
	(247.45, 71.41);

\path[draw=drawColor,line width= 0.5pt,line join=round] (142.55, 86.79) --
	(247.45, 86.79);

\path[draw=drawColor,line width= 0.5pt,line join=round] (142.55,102.17) --
	(247.45,102.17);

\path[draw=drawColor,line width= 0.5pt,line join=round] (142.55,117.55) --
	(247.45,117.55);

\path[draw=drawColor,line width= 0.5pt,line join=round] (162.57, 57.56) --
	(162.57,126.48);

\path[draw=drawColor,line width= 0.5pt,line join=round] (189.28, 57.56) --
	(189.28,126.48);

\path[draw=drawColor,line width= 0.5pt,line join=round] (215.98, 57.56) --
	(215.98,126.48);

\path[draw=drawColor,line width= 0.5pt,line join=round] (242.68, 57.56) --
	(242.68,126.48);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (147.31, 84.74) --
	(151.13, 84.06) --
	(154.94, 83.93) --
	(158.76, 83.97) --
	(162.57, 84.20) --
	(166.39, 84.27) --
	(170.20, 84.38) --
	(174.02, 86.20) --
	(177.83, 93.38) --
	(181.65,111.72);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (147.31, 62.86) --
	(151.13, 60.69) --
	(154.94, 60.69) --
	(158.76, 60.69);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (147.31, 72.23) --
	(151.13, 72.23) --
	(154.94, 72.23) --
	(158.76, 72.23) --
	(162.57, 72.23) --
	(166.39, 72.23) --
	(170.20, 72.23) --
	(174.02, 72.27) --
	(177.83, 72.70) --
	(181.65, 76.95) --
	(185.46, 89.66) --
	(189.28,106.37) --
	(193.09,123.35);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (147.31, 72.11) --
	(151.13, 72.11) --
	(154.94, 72.11) --
	(158.76, 72.11) --
	(162.57, 72.11) --
	(166.39, 72.11) --
	(170.20, 72.11) --
	(174.02, 72.15) --
	(177.83, 72.59) --
	(181.65, 76.89) --
	(185.46, 89.67) --
	(189.28,106.37) --
	(193.09,123.35);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (147.31, 84.74) circle (  1.96);

\path[fill=fillColor] (151.13, 84.06) circle (  1.96);

\path[fill=fillColor] (154.94, 83.93) circle (  1.96);

\path[fill=fillColor] (158.76, 83.97) circle (  1.96);

\path[fill=fillColor] (162.57, 84.20) circle (  1.96);

\path[fill=fillColor] (166.39, 84.27) circle (  1.96);

\path[fill=fillColor] (170.20, 84.38) circle (  1.96);

\path[fill=fillColor] (174.02, 86.20) circle (  1.96);

\path[fill=fillColor] (177.83, 93.38) circle (  1.96);

\path[fill=fillColor] (181.65,111.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 72.11) -- (150.09, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.31, 69.34) -- (147.31, 74.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.35, 72.11) -- (153.90, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.13, 69.33) -- (151.13, 74.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.17, 72.11) -- (157.72, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.94, 69.33) -- (154.94, 74.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.98, 72.11) -- (161.53, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.76, 69.33) -- (158.76, 74.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.80, 72.11) -- (165.35, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.57, 69.33) -- (162.57, 74.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.61, 72.11) -- (169.16, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.39, 69.33) -- (166.39, 74.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.43, 72.11) -- (172.98, 72.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.20, 69.34) -- (170.20, 74.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.24, 72.15) -- (176.79, 72.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.02, 69.37) -- (174.02, 74.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.06, 72.59) -- (180.61, 72.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.83, 69.81) -- (177.83, 75.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.87, 76.89) -- (184.42, 76.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.65, 74.12) -- (181.65, 79.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.69, 89.67) -- (188.24, 89.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.46, 86.90) -- (185.46, 92.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.50,106.37) -- (192.05,106.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.28,103.59) -- (189.28,109.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.32,123.35) -- (195.86,123.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.09,120.57) -- (193.09,126.12);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (147.31, 65.91) --
	(149.96, 61.33) --
	(144.67, 61.33) --
	cycle;

\path[fill=fillColor] (151.13, 63.74) --
	(153.77, 59.17) --
	(148.49, 59.17) --
	cycle;

\path[fill=fillColor] (154.94, 63.74) --
	(157.59, 59.17) --
	(152.30, 59.17) --
	cycle;

\path[fill=fillColor] (158.76, 63.74) --
	(161.40, 59.17) --
	(156.12, 59.17) --
	cycle;
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (145.35, 70.27) --
	(149.28, 70.27) --
	(149.28, 74.20) --
	(145.35, 74.20) --
	cycle;

\path[fill=fillColor] (149.17, 70.27) --
	(153.09, 70.27) --
	(153.09, 74.19) --
	(149.17, 74.19) --
	cycle;

\path[fill=fillColor] (152.98, 70.27) --
	(156.91, 70.27) --
	(156.91, 74.19) --
	(152.98, 74.19) --
	cycle;

\path[fill=fillColor] (156.80, 70.27) --
	(160.72, 70.27) --
	(160.72, 74.19) --
	(156.80, 74.19) --
	cycle;

\path[fill=fillColor] (160.61, 70.27) --
	(164.54, 70.27) --
	(164.54, 74.19) --
	(160.61, 74.19) --
	cycle;

\path[fill=fillColor] (164.43, 70.27) --
	(168.35, 70.27) --
	(168.35, 74.19) --
	(164.43, 74.19) --
	cycle;

\path[fill=fillColor] (168.24, 70.27) --
	(172.16, 70.27) --
	(172.16, 74.20) --
	(168.24, 74.20) --
	cycle;

\path[fill=fillColor] (172.05, 70.31) --
	(175.98, 70.31) --
	(175.98, 74.23) --
	(172.05, 74.23) --
	cycle;

\path[fill=fillColor] (175.87, 70.74) --
	(179.79, 70.74) --
	(179.79, 74.66) --
	(175.87, 74.66) --
	cycle;

\path[fill=fillColor] (179.68, 74.99) --
	(183.61, 74.99) --
	(183.61, 78.91) --
	(179.68, 78.91) --
	cycle;

\path[fill=fillColor] (183.50, 87.70) --
	(187.42, 87.70) --
	(187.42, 91.62) --
	(183.50, 91.62) --
	cycle;

\path[fill=fillColor] (187.31,104.41) --
	(191.24,104.41) --
	(191.24,108.33) --
	(187.31,108.33) --
	cycle;

\path[fill=fillColor] (191.13,121.39) --
	(195.05,121.39) --
	(195.05,125.31) --
	(191.13,125.31) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (143.50, 57.56) -- (143.50, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (147.31, 57.56) -- (147.31, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.13, 57.56) -- (151.13, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (154.94, 57.56) -- (154.94, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (158.76, 57.56) -- (158.76, 63.25);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (166.39, 57.56) -- (166.39, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (170.20, 57.56) -- (170.20, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (174.02, 57.56) -- (174.02, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (177.83, 57.56) -- (177.83, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (181.65, 57.56) -- (181.65, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (185.46, 57.56) -- (185.46, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (189.28, 57.56) -- (189.28, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (193.09, 57.56) -- (193.09, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (196.90, 57.56) -- (196.90, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (200.72, 57.56) -- (200.72, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (204.53, 57.56) -- (204.53, 63.25);
